---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covid19Tracker

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/adegu789/covid19Tracker.svg?branch=master)](https://travis-ci.com/adegu789/covid19Tracker)
<!-- badges: end -->

The goal of covid19Tracker is to make you aware of what Covid-19 is doing to the world

## Installation
#### You need to have R version 4.0.2
You can install the released version of covid19Tracker from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("covid19Tracker")
```
And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("adegu789/covid19Tracker")
```
## Website
### You may want to first check the website and see how to get started: https://adegu789.github.io/covid19Tracker/

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(covid19Tracker)
# Wrong format
period = c("5-6-2020","7-8-2020")
country = "US"
plot <- covid19Tracker::drawCovidPlot(period,country)

####
# You Got error because your date format is not Correct
# Correct format
period = c("05-06-2020","07-08-2020")
country = "US"
plot <- covid19Tracker::drawCovidPlot(period,country)
```

## Lets see an example of world map

```{r worldMap, warning=FALSE, error=FALSE}
map <- covid19Tracker::drawCovidMap("09-09-2020","Deaths")
map
```

## You can also embed plots, for example:

```{r plot, echo = FALSE}
p <- covid19Tracker::drawCovidPlot(c("04-05-2020","06-05-2020"),"US")
p
```
